MCR_Algae_Data_Cleaning

### 2024-11-26 Personal_Prelim_Code/mcr_algal_data_cleaning_final.Rmd
updated new species names for data with Julianna's most recent check

# Caulerpa peltata is outdated --> Caulerpa racemosa
data$Taxonomy_Substrate_Functional_Group[data$Taxonomy_Substrate_Functional_Group == "Caulerpa peltata"] <- "Caulerpa racemosa"

@@

# remove old levels
data <- droplevels(data)
levels(as.factor(data$Taxonomy_Substrate_Functional_Group)) # 84 levels

@@

not_algae <- c("Ascidian", "Bare Space", "Coral", "Coral Rubble", "Corallimorpharia", "Heteractis sp.", "Millepora platyphylla", "No data", "Sand", "Sacrophyton sp.", "Shell Debris", "Soft Coral", "Sponge", "Tridacna sp.", "Zooxanthellae")

@@

#writing one file so column names will work with Noam's code
write.csv(wide_alldata_filtered, "allbenthicdata_cleaned.csv", row.names = FALSE)

>>>>

### ADDING JULIANNA UPDATES HERE ###
data$Taxonomy_Substrate_Functional_Group[data$Taxonomy_Substrate_Functional_Group == "Chnoospora implexa"] <- "Pseudochnoospora implexa"

data$Taxonomy_Substrate_Functional_Group[data$Taxonomy_Substrate_Functional_Group == "Caulerpa pickeringii"] <- "Caulerpa webbiana"

data$Taxonomy_Substrate_Functional_Group[data$Taxonomy_Substrate_Functional_Group == "Boodlea kaeneana"] <- "Cladophoropsis membranacea"

data$Taxonomy_Substrate_Functional_Group[data$Taxonomy_Substrate_Functional_Group == "Dictyota divaricata"] <- "Dictyota cervicornis"

# Caulerpa peltata is outdated --> Caulerpa racemosa JULIANNA UPDATE = Caulerpa chemnitzia
data$Taxonomy_Substrate_Functional_Group[data$Taxonomy_Substrate_Functional_Group == "Caulerpa peltata"] <- "Caulerpa chemnitzia"

### EVERYTHING ELSE BELOW AS BEFORE ###

@@

# remove old levels
data <- droplevels(data)
levels(as.factor(data$Taxonomy_Substrate_Functional_Group)) # 84 levels --> 85 AFTER JULIANNA UPDATES

@@

not_algae <- c("Ascidian", "Bare Space", "Coral", "Coral Rubble", "Corallimorpharia", "Heteractis sp.", "Millepora platyphylla", "No data", "Sand", "Sarcophyton sp.", "Shell Debris", "Soft Coral", "Sponge", "Tridacna sp.", "Zooxanthellae")

@@

#writing one file so column names will work with Noam's code
write.csv(wide_alldata_filtered, "data/allbenthicdata_cleaned.csv", row.names = FALSE)
